---
title: "README"
output: html_document
---
*Corredor_comment= Hi Aimee Schulz! I would like to start my comment saying that the organization of this Readme.Rmd file is very well done and easy to follow. Good job! 
However, I must also tell you that I was a little confused at first to find it. Since all your output files are gathered together with this Readme file. I think if you make folders for your outputs it could make your Assigment folder easier to follow. I hope this comment doesn't bothered you. I just want to help you to improve your assigment organization files.*

# Final R Assignment
## Project Background

### Data Inspection

* Load the two data files you used for your UNIX assignment in R and inspect their context. Use as many
functions as you can to describe their structure and their dimensions (file size, number of columns, number of
lines, ect...). You don't have to limit yourselves to the functions we learned in class.
*As a reminder, the files are:
	 fang_et_al_genotypes.txt : a published SNP data set including maize, teosinte (i.e., wild maize),
and Tripsacum (a close outgroup to the genus Zea) individuals
	snp_position.txt : an additional data file that includes the SNP id (first column), chromosome
location (third column), nucleotide location (fourth column) and other information for the SNPs genotyped
in the fang_et_al_genotypes.txt file


### Part 1: Data Processing

Manipulate the two files in R in order to format them for a downstream analysis. During this process, we will
need to join these data sets so that we have both genotypes and positions in a series of input files. 
All our files will be formatted such that the first column is "SNP_ID", the second column is "Chromosome", the third column is "Position", and subsequent columns are genotype data from either maize or teosinte individuals.

* For maize (Group = ZMMIL, ZMMLR, and ZMMMR in the third column of the
fang_et_al_genotypes.txt file) we want 20 files in total:
	* 10 files (1 for each chromosome) with SNPs ordered based on increasing position values and with missing
data encoded by this symbol: ?
	* 10 files (1 for each chromosome) with SNPs ordered based on decreasing position values and with
missing data encoded by this symbol: -

* For teosinte (Group = ZMPBA, ZMPIL, and ZMPJA in the third column of the
fang_et_al_genotypes.txt file) we want 20 files in total:
	* 10 files (1 for each chromosome) with SNPs ordered based on increasing position values and with missing
data encoded by this symbol: ?
	* 10 files (1 for each chromosome) with SNPs ordered based on decreasing position values and with
missing data encoded by this symbol: -

* A total of 40 files will therefore be produced.

### Part 2: Visualization

* Plot the total number of SNPs in our dataset on each chromosome. What groups contribute most of these
SNPs?

* Create a new column to indicate whether a particular site is homozygous (has the same nucleotide on both
chromosomes (i.e., A/A, C/C, G/G, T/T) or heterozygous (otherwise)). Recode the missing data as NA. Sort
your dataframe using Group and Species_ID values. Make a graph that shows the proportion of homozygous
and heterozygous sites as well as missing data in each species (you won't be able to see species names) and
each group. For groups normalize the height of individual bars using one of the ggplot "position adjustments"
options.

* Visualize one other feature of the dataset. The choice is up to you!

## Project Script and Data
### Part 1

Load and inspect the fang_et_al_genotypes.txt and snp_position.txt files
```{r}
install.packages("ggplot2")
library(ggplot2)

fang <- read.table("fang_et_al_genotypes.txt")
snp <- read.table("snp_position.txt", header = TRUE, fill = TRUE)
object.size(fang)
typeof(fang)
class(fang)
str(fang)
dim(fang)
colnames(fang)

object.size(snp)
typeof(fang)
class(fang)
str(fang)
dim(snp)
colnames(snp)
```

*Corredor_comment= Nice job! that object.size function is a clever choice to describe the data *


## Format for a downstream analysis - join so that both genotypes and positions are in a series of input files
	First column SNP_ID, 2nd Chromosome, 3rd Position
```{r}
fnames <- unique(fang$Group)
fznames <- fnames[c(14,15,16)]
ftnames <- fnames[c(6,12,7)]
zfang <- fang[as.character(fang$Group) %in% fznames, ]
tfang <- fang[as.character(fang$Group) %in% ftnames, ]
```
**Corredor_comment= Interesting way to gathered Maize and Teosinte groups =)**


```{r}
tzea <- t(zfang)
dfzea <- as.data.frame(tzea, stringsAsFactors = FALSE)
dfzea$Sample_ID <- row.names(dfzea)
names(dfzea) <- as.character(dfzea[1,])
dfzea$Sample_ID
dfzea <- dfzea[4:986]
zeamerge <- merge(snp,dfzea,by.x = "SNP_ID",by.y = "Sample_ID")

tteo <- t(tfang)
dfteo <- as.data.frame(tteo, stringsAsFactors = FALSE)
dfteo$Sample_ID <- row.names(dfteo)
names(dfteo) <- as.character(dfteo[1,])
dfteo$Sample_ID
dfteo <- dfteo[4:986]
teomerge <- merge(snp,dfteo,by.x = "SNP_ID",by.y = "Sample_ID")
```

**Corredor_comment= About row.names() function it is necesary to create the new column Sample_ID. right? In order to merge by ID. Good job!*

Rearrange columns of teomerge and zeamerge to fit instructions


```{r}
teosort <- teomerge [,c(1, 3, 4, 2, 5:990)]
zeasort <- zeamerge [,c(1, 3, 4, 2, 5:1588)]
```

Sort by chromosomes, to be sorted in ascending order

**Corredor_comment= In this case I want to propose something to you*
**You know to make thinghs simple and prety :*
```
incTeosort<-teosort[order(as.numeric(as.character(teosort$Position))),]

for(i in 1:10){
  T_files<- incTeosort[incTeosort$Chromosome==i,]
  write.csv(T_files, sprintf("TChr_%d_",i),row.names=F )
}
```
**Corredor_comment= This is my example for the increasing order. It runs correctly**

```{r}
ZChr1 <- zeasort[zeasort$Chromosome == "1", ]
ZChr2 <- zeasort[zeasort$Chromosome == "2", ]
ZChr3 <- zeasort[zeasort$Chromosome == "3", ]
ZChr4 <- zeasort[zeasort$Chromosome == "4", ]
ZChr5 <- zeasort[zeasort$Chromosome == "5", ]
ZChr6 <- zeasort[zeasort$Chromosome == "6", ]
ZChr7 <- zeasort[zeasort$Chromosome == "7", ]
ZChr8 <- zeasort[zeasort$Chromosome == "8", ]
ZChr9 <- zeasort[zeasort$Chromosome == "9", ]
ZChr10 <- zeasort[zeasort$Chromosome == "10", ]

TChr10 <- teosort[teosort$Chromosome == "10", ]
TChr9 <- teosort[teosort$Chromosome == "9", ]
TChr8 <- teosort[teosort$Chromosome == "8", ]
TChr7 <- teosort[teosort$Chromosome == "7", ]
TChr6 <- teosort[teosort$Chromosome == "6", ]
TChr5 <- teosort[teosort$Chromosome == "5", ]
TChr4 <- teosort[teosort$Chromosome == "4", ]
TChr3 <- teosort[teosort$Chromosome == "3", ]
TChr2 <- teosort[teosort$Chromosome == "2", ]
TChr1 <- teosort[teosort$Chromosome == "1", ]
```

Sort by chromosomes, to be sorted in descending order

```{r}
ZChr1_des <- zeasort[zeasort$Chromosome == "1", ]
ZChr2_des <- zeasort[zeasort$Chromosome == "2", ]
ZChr3_des <- zeasort[zeasort$Chromosome == "3", ]
ZChr4_des <- zeasort[zeasort$Chromosome == "4", ]
ZChr5_des <- zeasort[zeasort$Chromosome == "5", ]
ZChr6_des <- zeasort[zeasort$Chromosome == "6", ]
ZChr7_des <- zeasort[zeasort$Chromosome == "7", ]
ZChr8_des <- zeasort[zeasort$Chromosome == "8", ]
ZChr9_des <- zeasort[zeasort$Chromosome == "9", ]
ZChr10_des <- zeasort[zeasort$Chromosome == "10", ]

TChr10_des <- teosort[teosort$Chromosome == "10", ]
TChr9_des <- teosort[teosort$Chromosome == "9", ]
TChr8_des <- teosort[teosort$Chromosome == "8", ]
TChr7_des <- teosort[teosort$Chromosome == "7", ]
TChr6_des <- teosort[teosort$Chromosome == "6", ]
TChr5_des <- teosort[teosort$Chromosome == "5", ]
TChr4_des <- teosort[teosort$Chromosome == "4", ]
TChr3_des <- teosort[teosort$Chromosome == "3", ]
TChr2_des <- teosort[teosort$Chromosome == "2", ]
TChr1_des <- teosort[teosort$Chromosome == "1", ]
```

Sort into ascending

```{r}
ZChr1_asc <- ZChr1[order(as.numeric(as.character(ZChr1$Position))), ]
ZChr2_asc <- ZChr2[order(as.numeric(as.character(ZChr2$Position))), ]
ZChr3_asc <- ZChr3[order(as.numeric(as.character(ZChr3$Position))), ]
ZChr4_asc <- ZChr4[order(as.numeric(as.character(ZChr4$Position))), ]
ZChr5_asc <- ZChr5[order(as.numeric(as.character(ZChr5$Position))), ]
ZChr6_asc <- ZChr6[order(as.numeric(as.character(ZChr6$Position))), ]
ZChr7_asc <- ZChr7[order(as.numeric(as.character(ZChr7$Position))), ]
ZChr8_asc <- ZChr8[order(as.numeric(as.character(ZChr8$Position))), ]
ZChr9_asc <- ZChr9[order(as.numeric(as.character(ZChr9$Position))), ]
ZChr10_asc <- ZChr10[order(as.numeric(as.character(ZChr10$Position))), ]

TChr1_asc <- TChr1[order(as.numeric(as.character(TChr1$Position))), ]
TChr2_asc <- TChr2[order(as.numeric(as.character(TChr2$Position))), ]
TChr3_asc <- TChr3[order(as.numeric(as.character(TChr3$Position))), ]
TChr4_asc <- TChr4[order(as.numeric(as.character(TChr4$Position))), ]
TChr5_asc <- TChr5[order(as.numeric(as.character(TChr5$Position))), ]
TChr6_asc <- TChr6[order(as.numeric(as.character(TChr6$Position))), ]
TChr7_asc <- TChr7[order(as.numeric(as.character(TChr7$Position))), ]
TChr8_asc <- TChr8[order(as.numeric(as.character(TChr8$Position))), ]
TChr9_asc <- TChr9[order(as.numeric(as.character(TChr9$Position))), ]
TChr10_asc <- TChr10[order(as.numeric(as.character(TChr10$Position))), ]
```


Sort into descending

```{r}
ZChr1_des <- ZChr1[order(as.numeric(as.character(ZChr1$Position)) , decreasing = TRUE), ]
ZChr2_des <- ZChr2[order(as.numeric(as.character(ZChr2$Position)) , decreasing = TRUE), ]
ZChr3_des <- ZChr3[order(as.numeric(as.character(ZChr3$Position)) , decreasing = TRUE), ]
ZChr4_des <- ZChr4[order(as.numeric(as.character(ZChr4$Position)) , decreasing = TRUE), ]
ZChr5_des <- ZChr5[order(as.numeric(as.character(ZChr5$Position)) , decreasing = TRUE), ]
ZChr6_des <- ZChr6[order(as.numeric(as.character(ZChr6$Position)) , decreasing = TRUE), ]
ZChr7_des <- ZChr7[order(as.numeric(as.character(ZChr7$Position)) , decreasing = TRUE), ]
ZChr8_des <- ZChr8[order(as.numeric(as.character(ZChr8$Position)) , decreasing = TRUE), ]
ZChr9_des <- ZChr9[order(as.numeric(as.character(ZChr9$Position)) , decreasing = TRUE), ]
ZChr10_des <- ZChr10[order(as.numeric(as.character(ZChr10$Position)) , decreasing = TRUE), ]

TChr1_des <- TChr1[order(as.numeric(as.character(TChr1$Position)) , decreasing = TRUE), ]
TChr2_des <- TChr2[order(as.numeric(as.character(TChr2$Position)) , decreasing = TRUE), ]
TChr3_des <- TChr3[order(as.numeric(as.character(TChr3$Position)) , decreasing = TRUE), ]
TChr4_des <- TChr4[order(as.numeric(as.character(TChr4$Position)) , decreasing = TRUE), ]
TChr5_des <- TChr5[order(as.numeric(as.character(TChr5$Position)) , decreasing = TRUE), ]
TChr6_des <- TChr6[order(as.numeric(as.character(TChr6$Position)) , decreasing = TRUE), ]
TChr7_des <- TChr7[order(as.numeric(as.character(TChr7$Position)) , decreasing = TRUE), ]
TChr8_des <- TChr8[order(as.numeric(as.character(TChr8$Position)) , decreasing = TRUE), ]
TChr9_des <- TChr9[order(as.numeric(as.character(TChr9$Position)) , decreasing = TRUE), ]
TChr10_des <- TChr10[order(as.numeric(as.character(TChr10$Position)) , decreasing = TRUE), ]
```

Replace "?/?" with "-/-" in descending files

```{r}
ZChr1_des[ZChr1_des == "?/?"] <- "-/-"
ZChr2_des[ZChr2_des == "?/?"] <- "-/-"
ZChr3_des[ZChr3_des == "?/?"] <- "-/-"
ZChr4_des[ZChr4_des == "?/?"] <- "-/-"
ZChr5_des[ZChr5_des == "?/?"] <- "-/-"
ZChr6_des[ZChr6_des == "?/?"] <- "-/-"
ZChr7_des[ZChr7_des == "?/?"] <- "-/-"
ZChr8_des[ZChr8_des == "?/?"] <- "-/-"
ZChr9_des[ZChr9_des == "?/?"] <- "-/-"
ZChr10_des[ZChr10_des == "?/?"] <- "-/-"

TChr1_des[TChr1_des == "?/?"] <- "-/-"
TChr2_des[TChr2_des == "?/?"] <- "-/-"
TChr3_des[TChr3_des == "?/?"] <- "-/-"
TChr4_des[TChr4_des == "?/?"] <- "-/-"
TChr5_des[TChr5_des == "?/?"] <- "-/-"
TChr6_des[TChr6_des == "?/?"] <- "-/-"
TChr7_des[TChr7_des == "?/?"] <- "-/-"
TChr8_des[TChr8_des == "?/?"] <- "-/-"
TChr9_des[TChr9_des == "?/?"] <- "-/-"
TChr10_des[TChr10_des == "?/?"] <- "-/-"
```

**Corredor_comment= In order to avoid this repetitive scripts I challengue you to look for a sapply or other functions that can make the work in just one line =)*

Remove "multiple" position rows
Located in: T2, T4, T7, T9
Z2, Z4, Z6, Z7, Z9

```{r}
TChr2_asc[TChr2_asc == "multiple"] <- NA
TChr2_asc <- TChr2_asc[!is.na(TChr2_asc$Position),]
TChr4_asc[TChr4_asc == "multiple"] <- NA
TChr4_asc <- TChr4_asc[!is.na(TChr4_asc$Position),]
TChr7_asc[TChr7_asc == "multiple"] <- NA
TChr7_asc <- TChr7_asc[!is.na(TChr7_asc$Position),]
TChr9_asc[TChr9_asc == "multiple"] <- NA
TChr9_asc <- TChr9_asc[!is.na(TChr9_asc$Position),]
TChr9_des[TChr9_des == "multiple"] <- NA
TChr9_des <- TChr9_des[!is.na(TChr9_des$Position),]
TChr7_des[TChr7_des == "multiple"] <- NA
TChr7_des <- TChr7_des[!is.na(TChr7_des$Position),]
TChr4_des[TChr4_des == "multiple"] <- NA
TChr4_des <- TChr4_des[!is.na(TChr4_des$Position),]
TChr2_des[TChr2_des == "multiple"] <- NA
TChr2_des <- TChr2_des[!is.na(TChr2_des$Position),]
ZChr2_des[ZChr2_des == "multiple"] <- NA
ZChr2_des <- ZChr2_des[!is.na(ZChr2_des$Position),]
ZChr4_des[ZChr4_des == "multiple"] <- NA
ZChr4_des <- ZChr4_des[!is.na(ZChr4_des$Position),]
ZChr6_des[ZChr6_des == "multiple"] <- NA
ZChr6_des <- ZChr6_des[!is.na(ZChr6_des$Position),]
ZChr7_des[ZChr7_des == "multiple"] <- NA
ZChr7_des <- ZChr7_des[!is.na(ZChr7_des$Position),]
ZChr9_des[ZChr9_des == "multiple"] <- NA
ZChr9_des <- ZChr9_des[!is.na(ZChr9_des$Position),]
ZChr9_asc <- ZChr9_asc[!is.na(ZChr9_asc$Position),]
ZChr9_asc[ZChr9_asc == "multiple"] <- NA
ZChr9_asc <- ZChr9_asc[!is.na(ZChr9_asc$Position),]
ZChr7_asc[ZChr7_asc == "multiple"] <- NA
ZChr7_asc <- ZChr7_asc[!is.na(ZChr7_asc$Position),]
ZChr6_asc[ZChr6_asc == "multiple"] <- NA
ZChr6_asc <- ZChr6_asc[!is.na(ZChr6_asc$Position),]
ZChr4_asc[ZChr4_asc == "multiple"] <- NA
ZChr4_asc <- ZChr4_asc[!is.na(ZChr4_asc$Position),]
ZChr2_asc[ZChr2_asc == "multiple"] <- NA
ZChr2_asc <- ZChr2_asc[!is.na(ZChr2_asc$Position),]
```

Remove excess columns besides the required ones

```{r}
TChr1_asc <- TChr1_asc[, -c(4:15)]
TChr2_asc <- TChr2_asc[, -c(4:15)]
TChr3_asc <- TChr3_asc[, -c(4:15)]
TChr4_asc <- TChr4_asc[, -c(4:15)]
TChr5_asc <- TChr5_asc[, -c(4:15)]
TChr6_asc <- TChr6_asc[, -c(4:15)]
TChr7_asc <- TChr7_asc[, -c(4:15)]
TChr8_asc <- TChr8_asc[, -c(4:15)]
TChr9_asc <- TChr9_asc[, -c(4:15)]
TChr10_asc <- TChr10_asc[, -c(4:15)]

TChr1_des <- TChr1_des[, -c(4:15)]
TChr2_des <- TChr2_des[, -c(4:15)]
TChr3_des <- TChr3_des[, -c(4:15)]
TChr4_des <- TChr4_des[, -c(4:15)]
TChr5_des <- TChr5_des[, -c(4:15)]
TChr6_des <- TChr6_des[, -c(4:15)]
TChr7_des <- TChr7_des[, -c(4:15)]
TChr8_des <- TChr8_des[, -c(4:15)]
TChr9_des <- TChr9_des[, -c(4:15)]
TChr10_des <- TChr10_des[, -c(4:15)]

ZChr1_asc <- ZChr1_asc[, -c(4:15)]
ZChr2_asc <- ZChr2_asc[, -c(4:15)]
ZChr3_asc <- ZChr3_asc[, -c(4:15)]
ZChr4_asc <- ZChr4_asc[, -c(4:15)]
ZChr5_asc <- ZChr5_asc[, -c(4:15)]
ZChr6_asc <- ZChr6_asc[, -c(4:15)]
ZChr7_asc <- ZChr7_asc[, -c(4:15)]
ZChr8_asc <- ZChr8_asc[, -c(4:15)]
ZChr9_asc <- ZChr9_asc[, -c(4:15)]
ZChr10_asc <- ZChr10_asc[, -c(4:15)]

ZChr1_des <- ZChr1_des[, -c(4:15)]
ZChr2_des <- ZChr2_des[, -c(4:15)]
ZChr3_des <- ZChr3_des[, -c(4:15)]
ZChr4_des <- ZChr4_des[, -c(4:15)]
ZChr5_des <- ZChr5_des[, -c(4:15)]
ZChr6_des <- ZChr6_des[, -c(4:15)]
ZChr7_des <- ZChr7_des[, -c(4:15)]
ZChr8_des <- ZChr8_des[, -c(4:15)]
ZChr9_des <- ZChr9_des[, -c(4:15)]
ZChr10_des <- ZChr10_des[, -c(4:15)]
```

Create files

```{r}
write.table(ZChr1_asc, "Chr1_Maize_ascending.txt", sep = "\t")
write.table(ZChr2_asc, "Chr2_Maize_ascending.txt", sep = "\t")
write.table(ZChr3_asc, "Chr3_Maize_ascending.txt", sep = "\t")
write.table(ZChr4_asc, "Chr4_Maize_ascending.txt", sep = "\t")
write.table(ZChr5_asc, "Chr5_Maize_ascending.txt", sep = "\t")
write.table(ZChr6_asc, "Chr6_Maize_ascending.txt", sep = "\t")
write.table(ZChr7_asc, "Chr7_Maize_ascending.txt", sep = "\t")
write.table(ZChr8_asc, "Chr8_Maize_ascending.txt", sep = "\t")
write.table(ZChr9_asc, "Chr9_Maize_ascending.txt", sep = "\t")
write.table(ZChr10_asc, "Chr10_Maize_ascending.txt", sep = "\t")

write.table(ZChr1_des, "Chr1_Maize_descending.txt", sep = "\t")
write.table(ZChr2_des, "Chr2_Maize_descending.txt", sep = "\t")
write.table(ZChr3_des, "Chr3_Maize_descending.txt", sep = "\t")
write.table(ZChr4_des, "Chr4_Maize_descending.txt", sep = "\t")
write.table(ZChr5_des, "Chr5_Maize_descending.txt", sep = "\t")
write.table(ZChr6_des, "Chr6_Maize_descending.txt", sep = "\t")
write.table(ZChr7_des, "Chr7_Maize_descending.txt", sep = "\t")
write.table(ZChr8_des, "Chr8_Maize_descending.txt", sep = "\t")
write.table(ZChr9_des, "Chr9_Maize_descending.txt", sep = "\t")
write.table(ZChr10_des, "Chr10_Maize_descending.txt", sep = "\t")

write.table(TChr1_asc, "Chr1_Teosinte_ascending.txt", sep = "\t")
write.table(TChr2_asc, "Chr2_Teosinte_ascending.txt", sep = "\t")
write.table(TChr3_asc, "Chr3_Teosinte_ascending.txt", sep = "\t")
write.table(TChr4_asc, "Chr4_Teosinte_ascending.txt", sep = "\t")
write.table(TChr5_asc, "Chr5_Teosinte_ascending.txt", sep = "\t")
write.table(TChr6_asc, "Chr6_Teosinte_ascending.txt", sep = "\t")
write.table(TChr7_asc, "Chr7_Teosinte_ascending.txt", sep = "\t")
write.table(TChr8_asc, "Chr8_Teosinte_ascending.txt", sep = "\t")
write.table(TChr9_asc, "Chr9_Teosinte_ascending.txt", sep = "\t")
write.table(TChr10_asc, "Chr10_Teosinte_ascending.txt", sep = "\t")

write.table(TChr1_des, "Chr1_Teosinte_descending.txt", sep = "\t")
write.table(TChr2_des, "Chr2_Teosinte_descending.txt", sep = "\t")
write.table(TChr3_des, "Chr3_Teosinte_descending.txt", sep = "\t")
write.table(TChr4_des, "Chr4_Teosinte_descending.txt", sep = "\t")
write.table(TChr5_des, "Chr5_Teosinte_descending.txt", sep = "\t")
write.table(TChr6_des, "Chr6_Teosinte_descending.txt", sep = "\t")
write.table(TChr7_des, "Chr7_Teosinte_descending.txt", sep = "\t")
write.table(TChr8_des, "Chr8_Teosinte_descending.txt", sep = "\t")
write.table(TChr9_des, "Chr9_Teosinte_descending.txt", sep = "\t")
write.table(TChr10_des, "Chr10_Teosinte_descending.txt", sep = "\t")

```

## Part 2

Create new file from total original data for the first graph
```{r}
trfang <- t(fang)
dffang <- as.data.frame(trfang, stringsAsFactors = FALSE)
dffang$Sample_ID <- row.names(dffang)
fangmerge <- merge(snp,dffang,by.x = "SNP_ID",by.y = "Sample_ID")
```
**Corredor_comment= this part is so exciting! Everithing is ready*

Remove multiples and unknowns

```{r}
fangmerge[fangmerge == "unknown"] <- NA
fangmerge[fangmerge == "multiple"] <- NA
fangmerge <- fangmerge[!is.na(fangmerge$Chromosome),]
```

Create bar plot based off of SNPs per Chromosome

```{r}
ggplot(fangmerge, aes(Chromosome), fill=Chromosome, color=chromosome) + geom_bar() + labs(title="Number of SNPs per Chromosome", y="SNP Count") + scale_x_discrete(limits=c(1,2,3,4,5,6,7,8,9,10))

```
**Corredor_comment= Nice first graph!*

Create the second graph comparing homozygosity and heterozygosity across species and groups

```{r}
fang_rm <- fang[, -c(2)]
melted_fang <- melt(fang_rm, id.vars = c("Sample_ID", "Group"))

values <- melted_fang$value

melted_fang[melted_fang == "A/A" | melted_fang == "C/C" | melted_fang == "T/T" | melted_fang == "G/G"] <- 0
melted_fang[melted_fang == "A/T" | melted_fang == "T/A" | melted_fang == "C/G" | melted_fang == "G/C" | melted_fang == "A/C"] <- 1
melted_fang[melted_fang == "?/?"] <- NA
melted_fang$Site <- row.names(melted_fang)
melted_fang$Site <- values
melted_fang[melted_fang == "?/?"] <- NA

Group <- melted_fang$Group
melted_fang <- melted_fang[,-c(2)]
melted_fang$Species_ID <- row.names(melted_fang)

melted_fang[sapply(melted_fang, is.factor)] <- lapply(melted_fang[sapply(melted_fang, is.factor)], as.character)

melted_fang[melted_fang == "ZMMIL" | melted_fang == "ZMMLR" | melted_fang == "ZMMMR"] <- "maize"
melted_fang[melted_fang == "ZMPBA" | melted_fang == "ZMPIL" | melted_fang == "ZMPJA"] <- "teosinte"

unique(melted_fang$Species_ID)
melted_fang[melted_fang == "TRIPS" | melted_fang == "ZDIPL" | melted_fang == "ZPERR" | melted_fang == "ZLUXR" | melted_fang == "ZMHUE" | melted_fang == "ZMXCH" | melted_fang == "ZMXCP" | melted_fang == "ZMXNO" | melted_fang == "ZMXNT" | melted_fang == "ZMXIL"] <- "tripsacum"

melted_fang[melted_fang == "0"] <- "homozygous"
melted_fang[melted_fang == "1"] <- "heterozygous"
melted_fang[melted_fang == "NA"] <- "unknown"

melted_fang$Group <- row.names(melted_fang)
melted_fang$Group <- Group

```

```{r}
ggplot(melted_fang, aes(x = Group, fill = melted_fang$value)) + geom_bar(position = "fill") + facet_grid(Species_ID ~ .) + labs(title = "Proportions of SNPs", x = "Group", y = "Proportion") + scale_fill_discrete(name = "Genotypes") + scale_x_discrete(limits = c("ZMMIL", "ZMMLR", "ZMMMR", "ZMPBA", "ZMPIL", "ZMPJA", "TRIPS", "ZDIPL", "ZLUXR", "ZMHUE", "ZMXCH", "ZMXCP", "ZMXIL", "ZMXNO", "ZMXNT", "ZPERR"))
```



Third plot - explore the distribution of SNP positions per Chromosome

```{r}
snp_rm <- snp[,c("Chromosome", "Position")]
snp_rm <- snp_rm[order(as.numeric(as.character(snp_rm$Position))), ]
ggplot(snp_rm, aes(x=Chromosome, y=Position)) + geom_point(size=1, color="grey") + labs(title = "Distribution of SNPs per Chromosome", x = "Chromosome", y="SNP Position") +ylab(NULL) + theme(axis.text.y = element_blank()) + scale_x_discrete(limits=c(1,2,3,4,5,6,7,8,9,10)) + geom_smooth(method='loess', se=FALSE, span=1/10) + scale_y_discrete(limits = NULL )
```

**Corredor_comment= It is interesting. What do you thing of triyng something like this:*
```
p <- ggplot(snp_rm, aes(x=Chromosome, y=Position)) + geom_point(size=1, color="grey")

```
**Corredor_comment=  You know, I think simple is more elegant* 

**Thanks for sharing!*
**=)*

